MSc Statistical Rob correction -Jan29

### 2018-02-01 MSc_Statistical_Rob_correction_-Jan29.Rmd
making sure computer and github are synched

---
title: "MSc Statistical overview"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    highlight: tango
    theme: cerulean
    toc: yes
  word_document:
    toc: yes
---
# Housekeeping
### Preamble

>>>>

---
title: "MSc Statistical Rob correction -Jan29"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    highlight: tango
    theme: cerulean
    toc: yes
  word_document:
    toc: yes
---
# Housekeeping
### Preamble
